Constraints on magic state protocols from the statistical mechanics of \\Wigner negativity

### 2021-06-29 magic_paper.tex
Minor typos/edits.

We note that this mapping to stochastic maps is not one-to-one. Not all stochastic maps on the phase space correspond to valid quantum operations. The reason is that the maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.

@@

In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$. The value $L_{\w|\r}(x) = 1$ is a global maximum. Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
\end{equation}
for all $x \in [0,1]$.
This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.

@@

\vspace{1cm}
\section{Acknowledgements}
We thank Earl Campbell, Matteo Lostaglio, Philippe Faist and Nicole Yunger Halpern for helpful comments and discussions. NK is supported by the EPSRC Centre for Doctoral Training in Controlled Quantum Dynamics. DJ is supported by the Royal Society and a University Academic Fellowship.

>>>>

We note however, that not all stochastic maps on the phase space correspond to valid quantum operations. The reason is that the maps must also respect the symplectic structure of the phase space, which is an additional non-trivial constraint.

@@

In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$. The value $L_{\w|\r}(x) = 1$ is a global maximum. Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components then it can be shown~\cite{ruch_mixing_1978} that
\begin{equation}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
\end{equation}
for all $x \in [0,1]$.
This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.

@@

\section{Acknowledgements}
We thank Earl Campbell, Matteo Lostaglio, Philippe Faist and Nicole Yunger Halpern for helpful comments and discussions. NK is supported by the EPSRC Centre for Doctoral Training in Controlled Quantum Dynamics. DJ is supported by the Royal Society and a University Academic Fellowship.
